Paper

### 2025-03-14 paper/paper.qmd
captions

```{r, include=FALSE}
posteriors <- abc_params_outbreak_control$unadj.values
comm_colonisation <- round(mean(posteriors[, "community-colonisation-rate"] * 100), 2)
outbreak_colonisation <- round(mean(posteriors[, "o-community-colonisation-rate"] * 100), 2)
outbreak_antibiotic_rate <- round(mean(posteriors[, "o-antibiotic-prescription-rate"] * 100), 2)
control_antibiotic_rate <- round(mean(posteriors[, "c-antibiotic-prescription-rate"] * 100), 2)
b_toilet_clean_rate <- round(mean(posteriors[, "toilet-cleaning-rate"]), 2)
o_toilet_clean_rate <- round(mean(posteriors[, "o-toilet-cleaning-rate"]), 2)
c_toilet_clean_rate <- round(mean(posteriors[, "c-toilet-cleaning-rate"]), 2)
```

@@

```{r tbl-posteriors, include=TRUE}
#| tbl-cap: "Summary of parameter posteriors after calibration using Approximate bayesian computation."
#| echo: false
params_table <- abc_params_outbreak_control$unadj.values %>% 
  as_tibble() %>% 
  mutate("community-colonisation-rate" = `community-colonisation-rate` * 100,
         "o-community-colonisation-rate" = `o-community-colonisation-rate` * 100,
         "o-antibiotic-prescription-rate" = `o-antibiotic-prescription-rate` * 100,
         "c-antibiotic-prescription-rate" = `c-antibiotic-prescription-rate` * 100) %>% 
  dplyr::select(!any_of(c("outbreak-start", "outbreak-end", "control-end"))) %>%
  dplyr::rename_with(.fn = \(.x) paste0("b-", .x), .cols = !starts_with("o-") & !starts_with("c-")) %>% 
  summarise(across(everything(), ~ paste0(
    round(mean(.x), 2),
    " (",
    round(sd(.x), 2),
    ")"
    )))

@@

```{r fig-abc-rates-retained-posterios, include=TRUE}
#| echo: false
#| label: fig-abc-rates-retained-posteriors
#| fig.cap: "Observed and simulated rates of _C. difficile_ infection over the simulated period. Approximate Bayesian computation was used to determine the unobserved parameters of the agent-based model. The red line shows the true observed infection rates. The black solid line shows the mean simulated rates; the dashed lines show the standard deviation."
#| fig.width: 18
#| fig.height: 8
ggplot(long_observed_ss, aes(x = x, y = rates)) + geom_line(color = 'red') +
  geom_line(data = sim_mean, aes(x = x, y = m)) +
  geom_line(data = sim_mean, aes(x = x, y = q_high), linetype='dashed') +
  geom_line(data = sim_mean, aes(x = x, y = q_low), linetype='dashed') + 
  theme(text=element_text(size=24)) +
  xlab("Date") + ylab("Rate (cases per 1000 patient days)")
```

@@

```{r fig-consts-sims-mean-sd, include=TRUE}
# plot but with mean and sd instead rather than individual
consts_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim) %>%
  summarise(m = mean(rate),
            q_high = quantile(rate, 0.75),
            q_low = quantile(rate, 0.25),
            .groups = "keep") %>%
  ggplot() +
  geom_line(aes(x = date_sim, y = m)) +
  geom_line(aes(x = date_sim, y = q_high), linetype='dashed') +
  geom_line(aes(x = date_sim, y = q_low), linetype='dashed') + 
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "red") +
  guides(color="none")
```

@@

The sensitivity analysis explored the impact of different infection control practices on the number of cases observed during the outbreak period -- the results are shown in @fig-sensitivity-analysis. The analysis showed that the cleaning of toilets had a dramatic impact on the number of cases observed during the outbreak period, although the benefit appeared to plateaeu beyond a certain amount -- for example, cleaning toilets more than twice per day appeared to have marginal benefits. The number of hospital acquired cases did not appear to be sensitive to the antimicrobial prescription rate during the outbreak period. The cohorting of patients into single-occupancy rooms after colonisation/infection had an almost linear relationship with the number of cases.

@@

```{r fig-sensitvity-pre-outbreak-abx, include=TRUE, eval=TRUE}
sens_abx_prescription_pre_outbreak_outbreak_cases %>% 
  group_by(`antibiotic-prescription-rate`) %>% 
  summarise(mean_cases = mean(`outbreak-cases`),
            sd_cases = sd(`outbreak-cases`)) %>% 
  ggplot(aes(x = `antibiotic-prescription-rate`, y = mean_cases)) +
  geom_line() + 
  # add sd
  geom_line(data = . %>% 
              mutate(upper = mean_cases + sd_cases,
                     lower = mean_cases - sd_cases),
            aes(y = upper), linetype = "dashed") +
  geom_line(data = . %>% 
              mutate(upper = mean_cases + sd_cases,
                     lower = mean_cases - sd_cases),
            aes(y = lower), linetype = "dashed")
```

>>>>

```{r text-vals, include=FALSE}
posteriors <- abc_params_outbreak_control$unadj.values
comm_colonisation <- round(mean(posteriors[, "community-colonisation-rate"] * 100), 2)
outbreak_colonisation <- round(mean(posteriors[, "o-community-colonisation-rate"] * 100), 2)
outbreak_antibiotic_rate <- round(mean(posteriors[, "o-antibiotic-prescription-rate"] * 100), 2)
control_antibiotic_rate <- round(mean(posteriors[, "c-antibiotic-prescription-rate"] * 100), 2)
b_toilet_clean_rate <- round(mean(posteriors[, "toilet-cleaning-rate"]), 2)
o_toilet_clean_rate <- round(mean(posteriors[, "o-toilet-cleaning-rate"]), 2)
c_toilet_clean_rate <- round(mean(posteriors[, "c-toilet-cleaning-rate"]), 2)
```

@@

```{r tbl-posteriors, include=TRUE}
#| tbl-cap: "Summary of parameter posteriors after calibration using approximate Bayesian computation."
#| echo: false
params_table <- abc_params_outbreak_control$unadj.values %>% 
  as_tibble() %>% 
  mutate("community-colonisation-rate" = `community-colonisation-rate` * 100,
         "o-community-colonisation-rate" = `o-community-colonisation-rate` * 100,
         "o-antibiotic-prescription-rate" = `o-antibiotic-prescription-rate` * 100,
         "c-antibiotic-prescription-rate" = `c-antibiotic-prescription-rate` * 100) %>% 
  dplyr::select(!any_of(c("outbreak-start", "outbreak-end", "control-end"))) %>%
  dplyr::rename_with(.fn = \(.x) paste0("b-", .x), .cols = !starts_with("o-") & !starts_with("c-")) %>% 
  summarise(across(everything(), ~ paste0(
    round(mean(.x), 2),
    " (",
    round(sd(.x), 2),
    ")"
    )))

@@

```{r fig-abc-rates-retained-posteriors, include=TRUE}
#| echo: false
#| label: fig-abc-rates-retained-posteriors
#| fig.cap: "Simulated rates of _C. difficile_ infection generated from the simulations retained after applying the rejection approximate Bayesian computation algorithm. The red line shows the true observed infection rates. The black solid line shows the median simulated rates; the dashed lines show the 25^th^ and 75^th^ quantiles."
#| fig.width: 18
#| fig.height: 8
ggplot(long_observed_ss, aes(x = x, y = rates)) + geom_line(color = 'red') +
  geom_line(data = sim_mean, aes(x = x, y = m)) +
  geom_line(data = sim_mean, aes(x = x, y = q_high), linetype='dashed') +
  geom_line(data = sim_mean, aes(x = x, y = q_low), linetype='dashed') + 
  theme(text=element_text(size=24)) +
  xlab("Date") + ylab("Rate (cases per 1000 patient days)")
```

@@

```{r fig-consts-sims-mean-sd, include=TRUE}
#| echo: false
#| fig-cap: "Simulated rates of _C. difficile_ infection generated by using the posterior parameter distributions. Input parameter samples were generated by sampling the uniform distribution $U_[\\mu - \\sigma, \\mu + \\sigma]$, where $\\mu$ and $\\sigma$ are the mean and standard deviation of the parameter's posterior distribution respectively. The red line shows the true observed infection rates. The black solid line shows the median simulated rates; the dashed lines show the 25^th^ and 75^th^ quantiles."
# plot but with mean and sd instead rather than individual
consts_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim) %>%
  summarise(m = median(rate),
            q_high = quantile(rate, 0.75),
            q_low = quantile(rate, 0.25),
            .groups = "keep") %>%
  ggplot() +
  geom_line(aes(x = date_sim, y = m)) +
  geom_line(aes(x = date_sim, y = q_high), linetype='dashed') +
  geom_line(aes(x = date_sim, y = q_low), linetype='dashed') + 
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "red") +
  guides(color="none")
```

```{r fig-single-outbreak-coloured, include=FALSE}
#| echo: false
#| fig.width: 18
#| fig.height: 8
#| message: false
single_outbreak_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  #slice_sample(n=10) %>% 
  dplyr::select(!`siminputrow`) %>% 
  pivot_longer(cols = !c(`random-seed`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim, `random-seed`) %>%
  summarise(rate = mean(rate)) %>%
  ggplot(aes(x = date_sim,
             y = rate,
             color = factor(`random-seed`))) +
  geom_line() +
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "black") +
  guides(color="none")
```

@@

```{r fig-posterior-predictive-check, include=TRUE}
#| echo: false
#| fig-cap: "Posterior predictive check of the model. Simulations were generated by sampling with replacement from the posterior parameter distributions after approximate Bayesian computation. Each simulation was run using different random number generators. The red line shows the true observed infection rates. The black solid line shows the median simulated rates; the dashed lines show the 25^th^ and 75^th^ quantiles."
posterior_predictive_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim) %>%
  summarise(m = median(rate),
            q_high = quantile(rate, 0.75),
            q_low = quantile(rate, 0.25),
            .groups = "keep") %>%
  ggplot() +
  geom_line(aes(x = date_sim, y = m)) +
  geom_line(aes(x = date_sim, y = q_high), linetype='dashed') +
  geom_line(aes(x = date_sim, y = q_low), linetype='dashed') + 
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "red") +
  guides(color="none")
```

```{r fig-posterior-predictive-check-coloured, include=FALSE}
#| echo: false
#| message: false
posterior_predictive_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  #slice_sample(n=10) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(siminputrow, date_sim) %>%
  summarise(rate = mean(rate)) %>%
  ggplot(aes(x = date_sim,
             y = rate,
             color = factor(`siminputrow`))) +
  geom_line() +
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "black") +
  guides(color="none")
```

The sensitivity analysis explored the impact of different infection control practices on the number of cases observed during the outbreak period -- the results are shown in @fig-sensitivity-analysis. The analysis showed that the cleaning of toilets had a dramatic impact on the number of cases observed during the outbreak period, although the benefit appeared to plateau beyond a certain amount -- for example, cleaning toilets more than twice per day appeared to have marginal benefits. The number of hospital acquired cases did not appear to be sensitive to the antimicrobial prescription rate during the outbreak period. The cohorting of patients into single-occupancy rooms after colonisation/infection had an almost linear relationship with the number of cases.

@@

```{r fig-sensitvity-pre-outbreak-abx, include=TRUE, eval=TRUE}
#| echo: false
sens_abx_prescription_pre_outbreak_outbreak_cases %>% 
  group_by(`antibiotic-prescription-rate`) %>% 
  summarise(mean_cases = mean(`outbreak-cases`),
            sd_cases = sd(`outbreak-cases`)) %>% 
  ggplot(aes(x = `antibiotic-prescription-rate`, y = mean_cases)) +
  geom_line() + 
  # add sd
  geom_line(data = . %>% 
              mutate(upper = mean_cases + sd_cases,
                     lower = mean_cases - sd_cases),
            aes(y = upper), linetype = "dashed") +
  geom_line(data = . %>% 
              mutate(upper = mean_cases + sd_cases,
                     lower = mean_cases - sd_cases),
            aes(y = lower), linetype = "dashed")
```
